Architectures and Open pNets

### 2018-11-09 2018-Arch-pNets/arch-pNets.tex
New drawing Failure Timer pNet

@@

We obtain the
synchronisation vector SV0 shown in \fig{enc:nopri}, where $b_0$ and
$b_1$ are the Boolean values associated to the actions encoding the
ports {\PortFail} and {\NameCtrl.\PortFail}, $\alpha_0$ is a fresh
action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
relation among ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
that, in our encoding, all three ports are present in the
synchronisation vector.  \Fig{enc:nopri} shows
the four synchronisation vectors SV0\ndash SV3 corresponding to the
connectors in \fig{schema:ArchFailure:BIP} and an additional vector
SV4, synchronising the {\init} transitions of the two pLTSs.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
  \caption{The pNET encoding the Failure Monitor architecture (without the priority model)}
  \label{fig:FailureTimer:pNet}
\end{figure}

@@

We obtain the
synchronisation vector SV0 shown in \fig{FailureTimer:pNet}, where $b_0$ and
$b_1$ are the Boolean values associated to the actions encoding the
ports {\PortFail} and {\NameCtrl.\PortFail}, $\alpha_0$ is a fresh
action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
relation among ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
that, in our encoding, all three ports are present in the
synchronisation vector.  \Fig{FailureTimer:pNet} shows
the four synchronisation vectors SV0\ndash SV3 corresponding to the
connectors in \fig{schema:ArchFailure:BIP} and an additional vector
SV4, synchronising the {\init} transitions of the two pLTSs.
